### 2022-08-30 poster_eccb22_barcelona/poster_eccb22_barcelona.tex
ENH progressed poster

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{multicol}
\usepackage{natbib}
\usepackage{pstricks,pst-grad}
\usepackage{subfigure}
\usepackage{hyperref}

@@

% MY FIGURES
% \myfig - replacement for \figure
% necessary, since in multicol-environment 171231_training_matrix.eps
% \figure won't work
\newcommand{\myfig}[3][0]{
\begin{center}
  \vspace{0.5cm}
  \includegraphics[width=#3\hsize,angle=#1]{#2}
  \nobreak\medskip
\end{center}}
%
% MY CAPTIONS
% \mycaption - replacement for \caption
% necessary, since in multicol-environment \figure and
% therefore \caption won't work
%\newcounter{figure}
\setcounter{figure}{1}
\newcommand{\mycaption}[1]{
  \vspace{0.25cm}
  \begin{quote}%\centering
    {{\bf Figure \arabic{figure}:} #1}
  \end{quote}
  \vspace{0.5cm}
  \stepcounter{figure}
}
% DEFINE FONT COMMANDS
\newcommand{\fontbody}{\Large}
%\newcommand{\fontbody}[1]{\textsf{#1}}
\newcommand{\fonttitle}[1]{\veryHuge \textsf{#1}} 
\newcommand{\fontheader}[1]{\Huge \textsf{#1}}

@@

\begin{center}
%\begin{pcolumn}{1}
\pbox{0.98\textwidth}{}{linewidth=2mm,framearc=0.3,linecolor=lightblue,fillstyle=gradient,gradangle=0,gradbegin=white,gradend=whiteblue,gradmidpoint=1.0,framesep=0.25em}{
\begin{minipage}[c][10cm][c]{0.1\textwidth}
  \begin{center}
    \includegraphics[width=12cm,angle=0]{img/logo_sciences.eps}
  \end{center}
\end{minipage}
\begin{minipage}[c][9cm][c]{0.7\textwidth}
  \begin{center}
%Microarray analysis of chicken and mouse presomitic mesoderm along the posterior-anterior axisS
%    {\sc \Huge Microarray analysis of chicken and mouse}\\[4.mm]
%    {\sc \Huge presomitic mesoderm along the posterior-anterior axis}\\[2.mm]
%\vspace{1cm}
    { \fonttitle{Analysis of gene regulatory properties} }\\[4.mm]
    { \fonttitle{underlying trait pleiotropy} }\\[2.mm]
    \huge Aitor Gonz\'alez$^*$\\[2.mm]
    \large TAGC Laboratory, Aix-Marseille Univ, INSERM UMR1090, 13288 Marseille, France\\[2.mm]
    \large $^*$Email: aitor.gonzalez@univ-amu.fr
  \end{center}
  \end{minipage}
\begin{minipage}[c][10cm][c]{0.1\textwidth}
  \begin{center}
    \includegraphics[width=12cm,angle=0]{img/logo_tagc_400x230_centered_1.eps}
    \includegraphics[width=12cm,angle=0]{img/logo_tagc_400x230_centered_1.eps}
  \end{center}
\end{minipage}
} % end pbox
%\end{pcolumn}
\end{center}

@@

\begin{enumerate}
\item Genome-wide association studies (GWAS) map genotypes to traits.
\item The IEU OpenGWAS project is a database of GWAS:\\ \url{https://gwas.mrcieu.ac.uk}
\item The large number of available GWAS have allowed to define pleiotropic regions in the genome (REF).
\item Most GWAS loci are non-coding but the gene regulatory basis of pleiotropy is well understood.
\item Expression quantitative trait loci (eQTL) map genotypes to expression phenotypes.
\item The EBI eQTL Catalogue is a database of uniformely processed eQTLs:\\ \url{https://www.ebi.ac.uk/eqtl}
\item The R package coloc performs colocalization tests between genetic traits:\\ \url{https://CRAN.R-project.org/package=coloc}
\end{enumerate}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURE 1
\begin{minipage}{1\columnwidth}
    \begin{center}
	    \begin{minipage}{0.6\columnwidth} 
		    \includegraphics[width=\columnwidth]{example-image-a}
	    \end{minipage}
	    \mycaption{\fontbody A set of pruned index SNPs in approximate linkage equilibrium is labeled as positive based on LD distance to associated SNPs from the GRASP database \citep{Leslie2014} and annotated with the LD distance to annotations. This training dataset is used for supervised classification based on the gradient boosting algorithm (XGBOOST software). Intergenic regions are annotated and scored with this model.}
    \end{center}
\end{minipage}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURE 2
\begin{minipage}{1\columnwidth}
    \begin{center}
	    \begin{minipage}{0.55\columnwidth} 
		    \includegraphics[width=\columnwidth]{example-image-a}
	    \end{minipage}
	    \begin{minipage}{0.35\columnwidth} 
		    \includegraphics[width=\columnwidth]{example-image-b}
	    \end{minipage}
	    \mycaption{\fontbody A GWAS SNP prediction model based on gene regulatory annotations. Left: AUC values of intergenic GWAS Catalog SNPs calculated with GWAVA, DeepSea and TAGOOS scores. Right: Odds ratio of GWAS Catalog SNP enrichment in TAGOOS-significant or cell-specific regulatory (TSS, promoter flanking region, weak or strong enhancer) chromatin state regions.}
    \end{center}
\end{minipage}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURE 3
\begin{minipage}{1\columnwidth}
    \begin{center}
	    \begin{center}
		    \begin{minipage}{0.45\columnwidth} 
			    \includegraphics[width=\columnwidth]{example-image-c}
		    \end{minipage}
		    \begin{minipage}{0.45\columnwidth} 
		    \mycaption{\fontbody Correlation of sample number of selected variables with the TAGOOS score. For each unseen GWAS Catalog SNPs, we calculated a sample proportion matrix with the proportion of samples out of the maximal sample number of a given molecular assay. Heatmap of the sample proportion matrix with the SNPs in the rows ordered by the TAGOOS score (Green column).}
		    \end{minipage}
	    \end{center}
    \end{center}
\end{minipage}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURE 3
\begin{minipage}{1\columnwidth}
    \begin{center}
	    \begin{center}
		    \begin{minipage}{0.5\columnwidth} 
			    \includegraphics[width=\columnwidth]{example-image-a}
		    \end{minipage}
		    \mycaption{\fontbody Percentage of unseen GWAS Catalog SNPs with significant and non-significant TAGOOS scores annotated with each transcriptional regulator from the ReMap database ordered by the decreasing percentage in significant TAGOOS SNPs ($P_{\text{Wilcox paired}}=2.2\times 10^{-16}$) \citep{Cheneby2017}.}
	    \end{center}
    \end{center}
\end{minipage}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURE 5
\begin{minipage}{1\columnwidth}
    \begin{center}
	    \begin{center}
		    \begin{minipage}{0.7\columnwidth} 
			    \includegraphics[width=\columnwidth]{example-image-b}
		    \end{minipage}
		    \mycaption{\fontbody Motif density computed with RSAT Matrix-scan in 10 nt bins in a 100 nt window around intergenic unseen GWAS Catalog SNPs split according to the TAGOOS significance and the reference versus alternative allele \citep{Medina-Rivera2015}}
	    \end{center}
    \end{center}
\end{minipage}

@@

\item We present a new method to learn a supervised model of associated SNPs based on regulatory features (Fig. 1).

@@

\footnotesize
\bibliographystyle{plain}
\bibliography{biblio}

>>>>

	\usepackage{amsmath}
	\usepackage{graphicx}
	\usepackage{epsfig}
	\usepackage{multicol}
	\usepackage{natbib}
	\usepackage{pstricks,pst-grad}
	\usepackage{subfigure}
	\usepackage{hyperref}
	\usepackage{csvsimple}

@@

	% MY FIGURES
	% \myfig - replacement for \figure
	% necessary, since in multicol-environment 171231_training_matrix.eps
	% \figure won't work
	\newcommand{\myfig}[3][0]{
	\begin{center}
	  \vspace{0.5cm}
	  \includegraphics[width=#3\hsize,angle=#1]{#2}
	  \nobreak\medskip
	\end{center}}
	%
	% MY CAPTIONS
	% \mycaption - replacement for \caption
	% necessary, since in multicol-environment \figure and
	% therefore \caption won't work

	%\newcounter{figure}
	\setcounter{figure}{1}
	\newcommand{\mycaptionfig}[1]{
	  \vspace{0.25cm}
	  \begin{quote}%\centering
	    {{\bf Figure \arabic{figure}:} #1}
	  \end{quote}
	  \vspace{0.5cm}
	  \stepcounter{figure}
	}

	%\newcounter{table}
	\setcounter{table}{1}
	\newcommand{\mycaptiontab}[1]{
	  \vspace{0.25cm}
	  \begin{quote}%\centering
	    {{\bf Table \arabic{table}:} #1}
	  \end{quote}
	  \vspace{0.5cm}
	  \stepcounter{figure}
	}

	% DEFINE FONT COMMANDS
	\newcommand{\fontbody}{\Large}
	%\newcommand{\fontbody}[1]{\textsf{#1}}
	\newcommand{\fonttitle}[1]{\veryHuge \textsf{#1}} 
	\newcommand{\fontheader}[1]{\Huge \textsf{#1}}

@@

	\begin{center}
	%\begin{pcolumn}{1}
	\pbox{0.98\textwidth}{}{linewidth=2mm,framearc=0.3,linecolor=lightblue,fillstyle=gradient,gradangle=0,gradbegin=white,gradend=whiteblue,gradmidpoint=1.0,framesep=0.25em}{
	\begin{minipage}[c][10cm][c]{0.1\textwidth}
	  \begin{center}
	    \includegraphics[width=12cm,angle=0]{img_tmp/logo_sciences.eps}
	  \end{center}
	\end{minipage}
	\begin{minipage}[c][9cm][c]{0.7\textwidth}
	  \begin{center}
	%Microarray analysis of chicken and mouse presomitic mesoderm along the posterior-anterior axisS
	%    {\sc \Huge Microarray analysis of chicken and mouse}\\[4.mm]
	%    {\sc \Huge presomitic mesoderm along the posterior-anterior axis}\\[2.mm]
	%\vspace{1cm}
	    { \fonttitle{Analysis of gene regulatory properties} }\\[4.mm]
	    { \fonttitle{underlying trait pleiotropy} }\\[2.mm]
	    \huge Aitor Gonz\'alez$^*$\\[2.mm]
	    \large TAGC Laboratory, Aix-Marseille Univ, INSERM UMR1090, 13288 Marseille, France\\[2.mm]
	    \large $^*$Email: aitor.gonzalez@univ-amu.fr
	  \end{center}
	  \end{minipage}
	\begin{minipage}[c][10cm][c]{0.1\textwidth}
	  \begin{center}
	    \includegraphics[width=12cm,angle=0]{img_tmp/logo_tagc_400x230_centered_1.eps}
	    \includegraphics[width=12cm,angle=0]{img_tmp/logo_tagc_400x230_centered_1.eps}
	  \end{center}
	\end{minipage}
	} % end pbox
	%\end{pcolumn}
	\end{center}

@@

	\begin{enumerate}
	\item Genome-wide association studies (GWAS) map genotypes to traits.
	\item The IEU OpenGWAS project is a database of GWAS:\\ \url{https://gwas.mrcieu.ac.uk}
	\item The large number of available GWAS have allowed to define pleiotropic regions in the genome (\citep{2019.Posthuma.Watanabe}).
	\item Most GWAS loci are non-coding but the gene regulatory basis of pleiotropy is well understood.
	\item Expression quantitative trait loci (eQTL) map genotypes to expression phenotypes.
	\item The EBI eQTL Catalogue is a database of uniformely processed eQTLs:\\ \url{https://www.ebi.ac.uk/eqtl}
	\item The R package coloc performs colocalization tests between genetic traits:\\ \url{https://CRAN.R-project.org/package=coloc}
	\end{enumerate}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 1 web interface
	\begin{minipage}{\columnwidth}
	    \begin{center}
		    \begin{minipage}{1\columnwidth} 
			    \includegraphics[width=\columnwidth]{img/web.eps}
		    \end{minipage}
		    \mycaptionfig{Web interface with the results of the colocalization pipeline for the most pleiotropic variant rs3184504.}
	    \end{center}
	\end{minipage}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% Tab 1: Winner variants
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	% full size table is table*
	\begin{minipage}{\columnwidth}
	   \begin{center}
	\scriptsize
	\csvreader[separator=tab,
	tabular=ccrrp{0.4\textwidth},
	head,
	table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Pos (hg38) & \bfseries Variant & \bfseries GWAS Categories\\\hline,
	]{../ms/fig/tab_rsid_most_pleiotropic.tsv}{}% use head of csv as column names
	{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolvi}% specify your coloumns here
	\large  % normal size
		    \mycaptiontab{Pleiotropic regions involving 5 or more GWAS categories. Genomic coordinates are given for the hg38 assembly.}
	    \end{center}
	\end{minipage}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 1
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/pltbar_x_per_variant_etissue_y_egene.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/pltbar_x_per_variant_egene_y_etissue.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/pltbar_x_per_variant_egene_etissue_y_gwas.eps}
		    \end{minipage}
		    \mycaptionfig{Count of eGenes per variant-tissue (\textbf{Left}), eTissues per variant-eGene (\textbf{Center}) and GWAS categories per variant-eGene-eTissue (\textbf{Right}).}
	    \end{center}
	\end{minipage}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 2 VEP
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/missense_variant.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/splice_region_variant.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/3_prime_UTR_variant.eps}
		    \end{minipage}
		    \mycaptionfig{Variant effect predictor (VEP) analysis as a function of the number of GWAS catategory number for three different consequences: Missense variant (Left), splice region variant (Center) and 3’ UTR variant (Right)}
	    \end{center}
	\end{minipage}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 2
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{center}
			    \begin{minipage}{0.35\columnwidth} 
				    \includegraphics[width=\columnwidth]{img_tmp/bxplt_remaptf_per_rsid_flank_0.eps}
			    \end{minipage}
			    \begin{minipage}{0.6\columnwidth} 
			    \mycaptionfig{Binding count of transcription factors in the region surrounding pleiotropic variants (Radius 50 bp) as a function of the GWAS category count. }
			    \end{minipage}
		    \end{center}
	    \end{center}
	\end{minipage}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 3
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{minipage}{1\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/graphical_summary.eps}
		    \end{minipage}
		    \mycaptionfig{Model of regulatory variant pleiotropy. I have investigated
	three possible mechanisms of pleiotropy. Left, Pleiotropic variants have more
	eGenes that result in more functions and more phenotypes. This might arise
	from an enrichment of pleiotropic variants in splicing or 3’ UTR regions.
	Center, I have also found that eGenes of pleiotropic variants are active
	in more etissues which result in more GWAS phenotypes. This might be
	explained from variants being bound by more transcription factors. Left
	Triplets of variant-eGene-eTissues are associated with more GWAS pheno-
	types, which directly affect the number of GWAS phenotypes. I have found
	that this might be explained by an enrichment of missense alleles.}
	    \end{center}
	\end{minipage}

@@

	\item A pipeline to colocalize eQTLs and GWAS variantsWe present a new method to learn a supervised model of associated SNPs based on regulatory features (Fig. 1).
	\item We present a new method to learn a supervised model of associated SNPs based on regulatory features (Fig. 1).

@@

	\normalsize
	\bibliographystyle{plain}
	\bibliography{../ms/ms_pleiotropy.bib}
